Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-03-30 paper/Forest_and_Water/Forest_and_Water.Rmd
version to publish 20220330

@@

Zhang_small <- read_csv("../../data/TablesZhangetal2017_small.csv")
Zhang_large <- read_csv("../../data/TablesZhangetal2017_large.csv") %>%
  mutate(Complete = 1,
         `Possible duplicate` = 0)
new_data <- read_csv("../../data/TableNewData.csv")
```

<!-- read in the ET data -->

```{r, echo = F, warning = F, message=F}
PET_large <- read_csv("../../data/largeET.csv")
PET_small <- read_csv("../../data/smallET.csv")

# drop columns and make sure the titles are the same
PET_large <- PET_large %>%
  rename(Latitude = Latitiude,
         E0 = rvalue_1,
         `Watershed #` = Watershed)

PET_small <- PET_small %>%
  select(site_name, lat, long, rvalue_1) %>%
  rename(Latitude = lat,
         Longitude = long,
         `Watershed #` = site_name,
         E0 = rvalue_1)

# 
PET_all <- bind_rows(PET_large, PET_small)
# There are 7 missing E0 values
# > PET_all$`Watershed #`[is.na(PET_all$E0)==T]
# [1]  38 278 269 243 236 299 250
```

@@

<!--now combine with E0 values -->
```{r, echo = F}
All_data <- left_join(All_data ,PET_all %>% select(-c(Longitude, Latitude)), by = "Watershed #")
All_data <- All_data %>%
  mutate(E0 = ifelse(is.na(E0.x)==T, E0.y, E0.x)) %>%
  select(-c(E0.x,E0.y)) #%>%
  #rename(Latitude = Latitude.x,
#         Longitude = Longitude.x)

# calculate dryness index
All_data <- All_data %>%
  mutate(Dryness = E0/Pa_mm)
```

>>>>

All the final data and analysis for this paper are located on github: [https://github.com/WillemVervoort/Forest_and_water](https://github.com/WillemVervoort/Forest_and_water) on the "publish" branch.

@@

Zhang_small <- read_csv("../../data/SmallCatchments_T2.csv")
Zhang_large <- read_csv("../../data/LargeCatchments_T1.csv")
new_data <- read_csv("../../data/NewCatchments_T3.csv")
```

@@

<!--now combine with E0 values -->
```{r, echo = F}
# calculate dryness index
All_data <- All_data %>%
  mutate(Dryness = E0/Pa_mm)
```
